%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------    
  \cventry
    {Student Principal Investigator - NASA Proposal Writing \& Evaluation Experience Academy} % Job title
    {National Aeronautics and Space Administration (NASA)} % Organization
    {Remote/California} % Location
    {Sep 2019 - Nov 2019} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Led a team of 7 college STEM major students to design and write a 7-page proposal about an "Advanced Virtual Reality Exercise System" that helps astronauts achieve 100\%+ prescribed exercise completion rate. 
      	\item Our proposal was one of the top 4 rated among around 15 proposals.
      	\item Learned the best practice of writing professional proposals and proposal evaluation procedures from NASA.
	\end{cvitems}
    }
   
   \cventry
    {NASA Lucy Student Pipeline Accelerator and Competency Enabler (L'SPACE) Mission Concept Academy} % Job title
    {} % Organization
    {} % Location
    {May 2019 - Aug 2019} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Remotely cooperated with STEM major students to design a mission concept of characterizing a hydrocarbon sea (mare) on Titan, the largest moon of Saturn, and write a 35-page Preliminary Design Review (PDR). 
      	\item Used JMARS (a Planetary GIS Software) to find the best landing site for our probe.
      	\item Learned mission procedures and protocols from NASA engineers and scientists.
	\end{cvitems}
    }
    
  % \cventry
  %   {Co-President} % Job title
  %   {Competitive Programming Club @ De Anza College} % Organization
  %   {Cupertino, California} % Location
  %   {May 2019 - Jan 2020} % Date(s)
  %   {
	% \begin{cvitems} % Description(s) of tasks/responsibilities
  %     	\item Won the 14th place out of 86 teams in 2019 ACM International Collegiate Programming Contest (ICPC) Pacific Northwest Division 2. 
  %     	\item Hosted weekly training sessions to help members hone their algorithm, data structure, and problem-solving skills. 
	% \end{cvitems}
  %   }  
    
  \cventry
    {Student Delegate} % Job title
    {Global Initiatives Symposium (GIS) in Taiwan at National Taiwan University (NTU)} % Organization
    {Taipei, Taiwan} % Location
    {Jul 2018} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Collaborated with team members to propose an AI system that mitigated overcrowding in emergency rooms by optimizing triage and providing medical referrals suggestion. 
      	\item Listened to inspiring speeches given by professionals and industry experts from around the world about AI, the platform economy, personalized learning, and micro power.
	\end{cvitems}
    }  
  
  \cventry
    {President} % Job title
    {Biology Club, Taipei Municipal Jianguo High School} % Organization
    {Taipei, Taiwan} % Location
    {Sep 2015 - Jun 2016} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Organized and ran a six-day biology summer camp consisting of lectures, visits, and activities. Our summer camp attracted around 120 junior high school students and was nominated for high school creative proposal competition held by the Tang Prize, receiving a subsidy of US\$3300. 
      	\item Managed more than 100 club members. More than 50 biology classes were offered by my club every semester.
	\end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
