%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Product Engineer} % Job title
    {Silicon Valley Career Women} % Organization
    {Sunnyvale, California} % Location
    {Oct 2019 - Present} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Used Final Cut Pro to edit videos for Women Leadership Enhancement video program.
      	\item Developed and enhanced video and audio products.
	\end{cvitems}
    }
    
  \cventry
    {Teaching Assistant} % Job title
    {De Anza Computer Science Department} % Organization
    {Cupertino, California} % Location
    {Apr 2019 - Jun 2020} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item In-class TA for Intermediate and Beginning Programming Methodologies in C++.
		\item Take notes during classes and gather extra learning resources for students.       
      	\item Resolve problems encountered by students in class or homework.
      	\item Design surveys and collect feedback, identify opportunities for improvement and execute effective strategies to address deficiencies.
	\end{cvitems}
    }
    
  \cventry
    {De Anza Flea Market Assistant} % Job title
    {De Anza Flea Market} % Organization
    {Cupertino, California} % Location
    {May 2019 - Jun 2020} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item rovide gate-keeping support, verify event tickets and vendor information, respond to inquiries about space location, and assist in the flea market operation.
	\end{cvitems}
    }
	  
  \cventry
    {Student Principal Investigator - NASA Proposal Writing \& Evaluation Experience Academy} % Job title
    {National Aeronautics and Space Administration (NASA)} % Organization
    {Remote/Online} % Location
    {Sep 2019 - Nov 2019} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Led a team of 7 college STEM students to design and write a 7-page proposal about an Advanced Virtual Reality Exercising System that helps astronauts achieve 100\%+ prescribed exercise completion rate. 
      	\item Our proposal was the top 4 rated proposals among around 20 proposals.
      	\item Learned the best practice of writing professional proposals and proposal evaluation procedures from NASA.
	\end{cvitems}
    }
    
  \cventry
    {Co-President} % Job title
    {Competitive Programming Club @ De Anza College} % Organization
    {Cupertino, California} % Location
    {May 2019 - Nov 2019} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Won the 14th place out of 86 teams in 2019 ACM International Collegiate Programming Contest (ICPC) Pacific Northwest Division 2. 
      	\item Hosted weekly training sessions to help members hone their algorithm, data structure, and problem-solving skills. 
	\end{cvitems}
    }    
    
    \cventry
    {NASA Lucy Student Pipeline Accelerator and Competency Enabler Virtual Academy} % Job title
    {National Aeronautics and Space Administration (NASA)} % Organization
    {Remote/Online} % Location
    {May 2019 - Aug 2019} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Remotely cooperated with STEM students to design a mission concept of characterizing a hydrocarbon sea (mare) on Saturn’s moon - Titan and write a 35-page Preliminary Design Review (PDR). 
      	\item Used JMARS (a Planetary GIS Software) to find the best landing site for our probe.
      	\item Learned mission procedures and protocols from NASA engineers and scientists. 
	\end{cvitems}
    }  
    
    \cventry
    {Student Delegate} % Job title
    {Global Initiatives Symposium (GIS) in Taiwan at National Taiwan University (NTU)} % Organization
    {Taipei, Taiwan} % Location
    {Jul 2018} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Collaborated with team members to propose an AI system that mitigated the overcrowding in emergency rooms by optimizing triage and providing medical referrals suggestion. 
      	\item Listened to inspiring speeches given by professionals and industry experts from around the world about AI, the platform economy, personalized learning, and micro power.
	\end{cvitems}
    }  
    
    \cventry
    {Taiwan Semiconductor Manufacturing Company Elite Camp} % Job title
    {Taiwan Semiconductor Manufacturing Company (TSMC)} % Organization
    {Hsinchu, Taiwan} % Location
    {Jul 2018} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Learned the cutting edge development and application of semiconductors and visited the TSMC Museum of Innovation. 
      	\item Interacted with employees at TSMC and professors working with TSMC.
	\end{cvitems}
    } 
    
     \cventry
    {Student Leader Delegation of ATUAM} % Job title
    {Association of Taiwan University Alumni in MACAU} % Organization
    {Shanghai, China} % Location
    {Jul 2018} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Proposed holding social activities in universities to stimulate the social atmosphere for students and build new connections for an entrepreneurship competition. 
      	\item Visited a cultural and creative park, the T-MAKERS incubator, and Shanghai Jiao Tong University.
	\end{cvitems}
    } 
    
    \cventry
    {President} % Job title
    {Biology Club, Taipei Municipal Jianguo High School} % Organization
    {Taipei, Taiwan} % Location
    {May 2015 - May 2016} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Organized and ran a six-day biology summer camp which consisted of lectures, visits, and activities. Our summer camp had around 120 junior high school students and was nominated for high school creative proposal competition held by the Tang Prize, receiving a subsidy of US\$3300. 
      	\item Managed more than 100 club members. More than 50 biology classes were offered by my club every semester.
	\end{cvitems}
    } 
    
    
%---------------------------------------------------------

\end{cventries}
